% !TEX root = main.tex
\chapter{Conclusions}
\label{conclusions}


% \addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
% \section{Conclusions and Future Work}
% \addtocontents{toc}{\protect\setcounter{tocdepth}{2}}
Convex Optimization based guidance and MPC algorithms are highly versatile and amenable to real-time implementation for the landing of space vehicles. The successive convexification implemented herein could be used as a trajectory generator, sequential guidance routine, guidance and feed-forward routine, or simply as an offline validation and mission design tool. Its ability to quickly generate dynamically feasible trajectories is impressive.

In the future, it may be interesting to apply a TVC bandwidth constraint to the system as well as state triggered constraints (STCs) for mission specific actions like initial ignition timing as shown in \cite{szmuk2018successivestcs}. The hypersonic reentry problem has hybrid-discrete dynamic switching events where the vehicle changes properties. For example, during entry, a capsule may shed its protective ablative shield and dawn a parachute for a deceleration phase. It may be interesting to explore trajectory optimization and discrete event timing using successive convexification and state triggered constraints. The MRP switching mechanism can easily be encoded with STCs and may yield interesting model predictive attitude slewing algorithms. Additionally, it could be valuable to tackle the ascent vehicle objective with active aerodynamic disturbances and safety constraints. The problem can be split up into a couple smaller in-plane and out-of-plane problems, making the full solutions easier and perhaps more computationally tractable.

It would be valuable to write this routine in C/C++ for small embedded single board computers (SBCs). These SBCs could be dedicated path planning computers for small landing testbeds, robotic platforms, and other GN\&C validation hardware.


Although the majority of this thesis is implementation and adaptation, I hope it serves as an example of the versatility and usefulness of the SCvx routine and its capabilities. It is evident that intelligent online optimization routines, like the one demonstrated in this thesis, will be invaluable in shaping the future of autonomous robotics, spacecraft, and real-time decision making.