\documentclass[modernstyle, 11pt]{thesis}

\usepackage[utf8]{inputenc}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{subcaption}
\usepackage{sidecap}
\usepackage{mathtools}
% \newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\usepackage{commath}
\usepackage{listings}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{algorithm}
\usepackage[linewidth=1pt]{mdframed}
\usepackage{algpseudocode}
\usepackage{longtable,tabularx}
\usepackage{amsmath,amsfonts,bm} % Math packages
\usepackage[framed,numbered,autolinebreaks,useliterate]{mcode}

\renewcommand*\arraystretch{.7}


%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%
\title{A Study of the Successive Convexification Optimal Control Method for the Powered Descent Guidance Problem}
\author{Pádraig~S.}{Lysandrou}
\otherdegrees{B.S. ECE, Cornell University, 2018}
\degree{Masters of Science}				%  #1 {long descr.}
	{M.S., Aerospace Engineering}		%  #2 {short descr.}
\dept{Department of}					%  #1 {designation}
	{Aerospace Engineering Sciences}	%  #2 {name}
\advisor{Prof.}							%  #1 {title}
	{Robert D. Braun}					%  #2 {name}
\reader{Dr.~Jay McMahon}				%  2nd person to sign thesis
\readerThree{Dr. Hanspeter Schaub}		%  3rd person to sign thesis
\abstract{  \OnePageChapter				% because it is very short

	
	add intro fluff kind of stff here

	This thesis focuses on the implementation and development of a 6 degree-of-freedom (DoF) guidance algorithm that solves the powered descent guidance (PDG) problem. I present a modified version of the Szmuk-Acikmese 6-DoF algorithm presented in \cite{szmuk2018successive}. I present a similar algorithm utilizing Modified Rodrigues Parameters (MRPs) as the attitude formalism. This simplifies the formation to three parameters, from four, and does not require a norm constrain a every time step. 

	????

	}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	In no particular order, to my loving family: Plato, Carolyn, Helena, Maria, and animals.
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
	Foremost, I am thankful to Dr. Robert D. Braun for his support and advising through my work at Colorado Boulder. I would like to thank Professor Jay McMahon and Professor Hanspeter Schaub for serving on my committee and for their fulfilling coursework and advising. Additionally, I would like to thank Dr. Mason Peck for his four years of support at Cornell, which serve as my foundation in this field.

	I am also grateful for the insightful and thrilling technical discussions I have had with Sven Niederberger, Benjamin Chung, Janis Maczijewski, Joe Barnard, Miki Szmuk, Skye Mceowen, Ian Garcia, Shez Virani, Daniel Aguilar-Marsillach, the EsDL research team, and many more.
	
	Similarly, I would like to thank my SpaceX colleagues for grounding me in reality while letting me play with vehicles of the heavens. Go Falcon, Dragon, and Starlink!
	}

% \IRBprotocol{E927F29.001X}	% optional!
% \ToCisShort	% use this only for 1-page Table of Contents
% \LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures
% \LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\input chapter1.tex
\input chapter2.tex	
\input chapter3.tex
\input chapter4.tex
\input chapter5.tex
\input chapter6.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{plain}		% or "siam", or "alpha", etc.
\nocite{*}						% list all refs in database, cited or not
\bibliography{references}		% Bib database in "refs.bib"


%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix
\input appendixA.tex
% \input appendixB.tex


\end{document}

