\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage[utf8]{inputenc}
\usepackage{subcaption}
\usepackage{sidecap}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{listings}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{algorithm}
\usepackage[linewidth=1pt]{mdframed}
\usepackage{algpseudocode}
\usepackage{longtable,tabularx}
\usepackage{amsmath,amsfonts,bm} % Math packages

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Development of Successive Convexification Method for the Powered Descent Guidance Problem}
\author{Pádraig~S.}{Lysandrou}
\otherdegrees{B.S. ECE, Cornell University, 2018}
\degree{Masters of Science}		%  #1 {long descr.}
	{M.S., Aerospace Engineering}		%  #2 {short descr.}
\dept{Department of}			%  #1 {designation}
	{Aerospace Engineering Sciences}		%  #2 {name}
\advisor{Prof.}				%  #1 {title}
	{Robert D. Braun}			%  #2 {name}
\reader{Dr.~Jay McMahon}		%  2nd person to sign thesis
\readerThree{???}				%  3rd person to sign thesis
\abstract{  \OnePageChapter	% because it is very short

	INPUT ABSTRACT HERE
	}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	In no particular order, to my loving family: Plato, Carolyn, Helena, and Maria.
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
	I should begin with thanking Dr. Robert Braun for his support and advising through my Masters at Colorado Boulder. I would like to thank Professor Jay McMahon and Professor Hanspeter Schaub for serving on my committee and for their fulfilling coursework and advising. Additionally, I would like to thank Dr. Mason Peck for his four years of support at Cornell. I attribute most of my useful spacecraft engineering skills to the countless late nights spent on his projects.
	
	Similarly, I would like to thank my SpaceX colleagues for grounding me in reality while letting me play with vehicles of the heavens. Go Falcon, Dragon, and Starlink!
	}
% \IRBprotocol{E927F29.001X}	% optional!

\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex
\input chapter1.tex
\input chapter2.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{plain}	% or "siam", or "alpha", etc.
\nocite{*}		% list all refs in database, cited or not
\bibliography{references}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix
\input appendixA.tex
\input appendixB.tex


\end{document}

