\documentclass[modernstyle, 11pt]{thesis}

\usepackage[utf8]{inputenc}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{subcaption}
\usepackage{sidecap}
\usepackage{mathtools}
% \newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\usepackage{commath}
\usepackage{listings}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{algorithm}
\usepackage[linewidth=1pt]{mdframed}
\usepackage{algpseudocode}
\usepackage{longtable,tabularx}
\usepackage{amsmath,amsfonts,bm} % Math packages
\usepackage[framed,numbered,autolinebreaks,useliterate]{mcode}

\renewcommand*\arraystretch{.7}


%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%
\title{A Successive Convexification Optimal Guidance Implementation for the Pinpoint Landing of Space Vehicles}
\author{Pádraig~S.}{Lysandrou}
\otherdegrees{B.S. ECE, Cornell University, 2018}
\degree{Masters of Science}				%  #1 {long descr.}
	{M.S., Aerospace Engineering}		%  #2 {short descr.}
\dept{Department of}					%  #1 {designation}
	{Aerospace Engineering Sciences}	%  #2 {name}
\advisor{Prof.}							%  #1 {title}
	{Robert D. Braun}					%  #2 {name}
\reader{Dr.~Jay McMahon}				%  2nd person to sign thesis
\readerThree{Dr. Hanspeter Schaub}		%  3rd person to sign thesis
\abstract{  \OnePageChapter				% because it is very short

	Autonomous propulsive spacecraft have enabled the exploration of other planets, moons, asteroids, and other celestial bodies. Recent advances in real-time optimal guidance algorithms allow spacecraft to perform precision landing maneuvers enabling a new age of autonomous and crewed missions. These algorithms compute trajectories that are locally optimal to a given objective and are able to account for key mission aspects and dynamic constraints. Therefore, these methods can maximize the agility, and in this case, the divert capability of space vehicles subject to environmental dispersions while they are maneuvering to their terminal destinations.

	This thesis focuses on the implementation and development of a 6 degree-of-freedom (DoF) free-final-time guidance algorithm that solves the powered descent guidance (PDG) problem subject to vehicular, environmental, and mission constraints. A solution to this problem utilizing the successive convexification nonlinear Model Predictive Control (MPC) framework and modified Rodrigues parameters (MRPs) as the attitude formalism is presented. 
}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	In no particular order, to my loving family: Plato, Carolyn, Helena, Maria, and animals.
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
Foremost, I am thankful to Dr. Robert D. Braun for his support and advising through my work at Colorado Boulder. I would like to thank Professor Jay McMahon and Professor Hanspeter Schaub for serving on my committee and for their fulfilling coursework and advising. Additionally, I would like to thank Dr. Mason Peck for his four years of support at Cornell, which serve as my foundation in this field.

As an unordered set, I am grateful for the insightful technical discussions I have had with Shez Virani, Daniel Aguilar-Marsillach, the EsDL research team, Sven Niederberger, Benjamin Chung, Janis Maczijewski, Behçet Açikmeşe, Miki Szmuk, Skye Mceowen, Ian Garcia, Joe Barnard, and many more. Similarly, I would like to thank my SpaceX colleagues for grounding me in reality while letting me play with vehicles of the heavens. Go Falcon, Dragon, and Starlink!
}

% \IRBprotocol{E927F29.001X}	% optional!
% \ToCisShort	% use this only for 1-page Table of Contents
% \LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures
% \LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\input chapter1.tex
\input chapter2.tex	
\input chapter3.tex
\input chapter4.tex
\input chapter5.tex
\input chapter6.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{plain}		% or "siam", or "alpha", etc.
\nocite{*}						% list all refs in database, cited or not
\bibliography{references}		% Bib database in "refs.bib"


%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix
\input appendixA.tex
% \input appendixB.tex


\end{document}

